---
title: "Untitled"
author: "Udochi"
date: "February 28, 2018"
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results = FALSE)
library(tidyverse)
library(tidyr)
```

#10.5.What does tibble::enframe() do? When might you use it?
# **It converts heterogenous data types such as lists and atomic vectors to two column data frames.it can be used when organizing a list of data into data frames. The '?tibble::enframe function gives a detailed description.Below are some examples.**
```{r  results=FALSE}
x <- c(1,2,3,5,6)
enframe(x, name = "name", value = "value")
enframe(c(a = 5, b = 7))

```

#12.3.I claimed that iso2 and iso3 were redundant with country. Confirm this claim.
#**The columns were abbreviated versions of the country for each test data, so it is unneccessary to have the same records in three different columns.**
```{r}
H1 <- who %>% 
  gather(new_sp_m014:newrel_f65,key="key",
         value = "cases",
         na.rm =TRUE)

H4<- select(H1,country,iso2,iso3) %>% 
  distinct() %>% 
  group_by(country)
H4
  
```
#12.4.For each country, year, and sex compute the total number of cases of TB. Make an informative visualisation of the data

```{r echo =FALSE}
tidyr::who

H1 <- who %>%
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases", na.rm = TRUE)
H2 <- H1 %>%  mutate(key = stringr::str_replace(key, "newrel", "new_rel"))
H3 <- H2 %>% separate(key,c("new","type","sexage"),sep ="_") 
H4 <- H3 %>% select(-new,-iso2,-iso3)
H5 <- H4 %>% separate(sexage,c("sex","age"),sep =1)
H6 <- H5 %>% group_by(country, year, sex) %>%
  filter(year > 1995) %>%
  summarise(cases = sum(cases)) %>%
  unite(country_sex, country, sex, remove = FALSE) %>%
  ggplot(aes(x = year, y = cases, group = country_sex, colour = sex)) +
  geom_line()
H6
```